MultiDataImportPico

### 2023-12-14 Code/MultiDataImportPico.Rmd
test
test commit

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "ImportedMCData")

# number of rows to skip upon read csv
Skip <- 20

@@

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"

>>>>

# Set Project Variables
```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
 # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")

DataOut <- file.path("..","Data", "ImportedData", "ImportedMCData")

# number of rows to skip upon read csv
Skip <- 20
```

@@

TargetFile <- "20231207_PICO_MCMIX004_RUN131.csv"
